Analyzing X-ray images in Python with scikit-image

### 2016-08-21 skimage_tomo.tex
Reference papers that have cited scikit-image

Estimating the number of active users of an open-source package is a
difficult task. Download statistics, for example, largely
overestimate the number of active users, all the more if the package is
bundled with others in a software distribution, such as Anaconda or
Canopy. A view closer to reality can be obtained by analyzing the
statistics of visits of the online help, available on the project
website.  As of the first half of 2016, 20000 unique visitors visited the
\texttt{scikit-image} website every month at \url{http://scikit-image.org/}. These
users come from 80 countries, located almost equally in Europe, America
and Asia (with Oceania and Africa representing a much smaller fraction of
visitors).

@@

The authors gratefully acknowledge the work of the contributors of
  \texttt{scikit-image}. E. Gouillart acknowledges the support of ANR
  project EDDAM ANR-11-BS09-027.

>>>>

Estimating the number of active users of an open-source package is a
difficult task. Download statistics, for example, largely
overestimate the number of active users, all the more if the package is
bundled with others in a software distribution, such as Anaconda or
Canopy. A view closer to reality can be obtained by analyzing the
statistics of visits of the online help, available on the project
website.  As of the first half of 2016, 20000 unique visitors visited the
\texttt{scikit-image} website every month at
\url{http://scikit-image.org/}, from 138 countries.

The \texttt{scikit-image} paper of 2014 has been cited by 120 research
works (as of August 2016, according to Google Scholar), among which
studies that used X-ray imaging in fields such as medical imaging
\citep{Shen2015, Malan2016, Blackledge2016}, materials science
\citep{Bouttes2015} or geoscience \citep{Schluter2014}.

@@

The authors gratefully acknowledge the work of the contributors of
  \texttt{scikit-image}, and thank S. Deville and D. Vandembroucq for a
  careful reading of the paper and useful suggestions. E. Gouillart
  acknowledges the support of ANR project EDDAM ANR-11-BS09-027.
